Architectures and Open pNets

### 2018-10-18 2018-Arch-pNets/arch-pNets.tex
Arch-pNet paper: further modifications in response to comments by Ludo: moved the explanation of how transitions marked by false are used to simulate non-participation of ports in an interaction (added a reference to Milner for the construction)

Intuitively, we 1)~introduce a fresh initial state with an additional
$\init$ transition that initialises all the variables to those defined
by the initial valuation $\val{0}{C}$ of $C$, 2)~define a pNet action algebra that associates, as action parameter, an
additional Boolean value to each port, 3)~create pNet transitions that reflect the original transitions of
$C$ with $\true$ as parameter and 4)~create additional loop transitions marked by
$\false$.

@@

In order to encode these interactions using only one synchronisation vector, we use
the additional Boolean values associated to each port by the encoding
of coordinator components.  We observe that the three ports in this
connector form a ``causality chain'': {\NameCtrl.\PortFail} can only
participate in the interaction if the dangling port {\PortFail}
participates, which in turn can only participate if
{\NameTimer.\PortTick} does so.  These dependencies can be rewritten
as Boolean implications $\NameCtrl.\PortFail \Rightarrow \PortFail$
and $\PortFail \Rightarrow \NameTimer.\PortTick$.  However, notice
that, within the scope of this connector, {\NameTimer.\PortTick}
participates in all the interactions, meaning that the latter
implication is a tautology and can be discarded.  Thus, we obtain the
synchronisation vector SV0 shown in \fig{enc:nopri}, where $b_0$ and
$b_1$ are the Boolean values associated to the actions encoding the
ports {\PortFail} and {\NameCtrl.\PortFail}, $\alpha_0$ is a fresh
action name.  The guard $b_1 \Rightarrow b_0$ encodes the causal
relation among ports {\NameCtrl.\PortFail} and {\PortFail}.  Notice
that, in our encoding, all three ports are present in the
synchronisation vector.  Non-participation of a port corresponds to
firing the loop transition marked by \false.  \Fig{enc:nopri} shows
the four synchronisation vectors SV0\ndash SV3 corresponding to the
connectors in \fig{schema:ArchFailure:BIP} and an additional vector
SV4, synchronising the {\init} transitions of the two pLTSs.

>>>>

Intuitively, we 1)~introduce a fresh initial state with an additional
$\init$ transition that initialises all the variables to those defined
by the initial valuation $\val{0}{C}$ of $C$, 2)~define a pNet action algebra that associates, as action parameter, an
additional Boolean value to each port, 3)~create pNet transitions that reflect the original transitions of
$C$ with $\true$ as parameter and 4)~create additional loop transitions marked by
$\false$.
%
The loop transitions marked by $\false$ will be used in the encoding
of connectors.  Each BIP connector can define several interactions,
\ie ports involved in a connector need not necessarily always
participate.  On the contrary, each action in a pNet synchronisation
vector must participate in the synchronisation.  To address this
difference, we use the classical~\cite{milner83-calculi} approach,
whereby non-participation of a port in an interaction is simulated
by an additional loop transition.

@@

In order to encode these interactions using only one synchronisation vector, we use
the additional Boolean values associated to each port by the encoding
of coordinator components.  We observe that the three ports in this
connector form a ``causality chain'': {\NameCtrl.\PortFail} can only
participate in the interaction if the dangling port {\PortFail}
participates, which in turn can only participate if
{\NameTimer.\PortTick} does so.  These dependencies can be rewritten
as Boolean implications $\NameCtrl.\PortFail \Rightarrow \PortFail$
and $\PortFail \Rightarrow \NameTimer.\PortTick$.  However, notice
that, within the scope of this connector, {\NameTimer.\PortTick}
participates in all the interactions, meaning that the latter
implication is a tautology and can be discarded.  Thus, we obtain the
synchronisation vector SV0 shown in \fig{enc:nopri}, where $b_0$ and
$b_1$ are the Boolean values associated to the actions encoding the
ports {\PortFail} and {\NameCtrl.\PortFail}, $\alpha_0$ is a fresh
action name.  The guard $b_1 \Rightarrow b_0$ encodes the causal
relation among ports {\NameCtrl.\PortFail} and {\PortFail}.  Notice
that, in our encoding, all three ports are present in the
synchronisation vector.  \Fig{enc:nopri} shows
the four synchronisation vectors SV0\ndash SV3 corresponding to the
connectors in \fig{schema:ArchFailure:BIP} and an additional vector
SV4, synchronising the {\init} transitions of the two pLTSs.
